Manuscript Figures

### 2024-12-13 Manuscript_Figures.Rmd
Plot biomass of small trees

```{r}
library(here)
library(tidyverse)
library(terra)
library(tidyterra)
library(ggthemes)
library(ggpattern)
library(sf)
```

@@

### Stacked bar chart of species composition in burn plot
```{r}
bp_mapcodes <- unique(as.vector(values(crop(IC_map, bp4))))
BA_plot <- before_after %>% 
  filter(MapCode %in% bp_mapcodes) %>%
  group_by(pre_post, SpeciesName) %>%
  summarize(CohortAge_Avg = mean(CohortAge),
            CohortBiomass_Sum = sum(CohortBiomass)) %>%
  mutate(pre_post = factor(pre_post, levels = c("Initial Conditions",
                                                "Fire2-Dry",
                                                "Fire2-Wet",
                                                "Fire5-Dry",
                                                "Fire5-Wet",
                                                "No Scrapple"))) %>%
  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
                                 SpeciesName=="SlashPine" ~ "Slash Pine",
                                 SpeciesName=="TulipTree" ~ "Tulip Poplar",
                                 SpeciesName=="RedMaple" ~ "Red Maple",
                                 SpeciesName=="SweetGum" ~ "Sweetgum",
                                 SpeciesName=="WhiteOak" ~ "White Oak",
                                 SpeciesName=="TurkeyOak" ~ "Turkey Oak",
                                 SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
  mutate(SpeciesName = factor(SpeciesName,
                              levels = c(
                                "White Oak",
                                "Turkey Oak",
                                "Sweetgum",
                                "Red Maple",
                                "Shortleaf Pine",
                                "Slash Pine",
                                "Loblolly Pine",
                                "Longleaf Pine",
                                "Tulip Poplar"
                              )))

@@

>>>>

```{r}
library(here)
library(tidyverse)
library(terra)
library(tidyterra)
library(ggthemes)
library(ggpattern)
library(sf)
library(patchwork)
```

@@

### Stacked bar chart of species composition in burn plot
```{r}
bp_mapcodes <- unique(as.vector(values(crop(IC_map, bp4))))
BA_plot <- before_after %>% 
  filter(MapCode %in% bp_mapcodes) %>%
  group_by(pre_post, SpeciesName) %>%
  summarize(CohortAge_Avg = mean(CohortAge),
            CohortBiomass_Sum = sum(CohortBiomass)) %>%
  mutate(pre_post = factor(pre_post, levels = c("Initial Conditions",
                                                "Fire2-Dry",
                                                "Fire2-Wet",
                                                "Fire5-Dry",
                                                "Fire5-Wet",
                                                "No Scrapple"),
                           labels = c("Initial Conditions",
                                      "Fire2-Dry",
                                      "Fire2-Wet",
                                      "Fire5-Dry",
                                      "Fire5-Wet",
                                      "NoFire-Wet"))) %>%
  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
                                 SpeciesName=="SlashPine" ~ "Slash Pine",
                                 SpeciesName=="TulipTree" ~ "Tulip Poplar",
                                 SpeciesName=="RedMaple" ~ "Red Maple",
                                 SpeciesName=="SweetGum" ~ "Sweetgum",
                                 SpeciesName=="WhiteOak" ~ "White Oak",
                                 SpeciesName=="TurkeyOak" ~ "Turkey Oak",
                                 SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
  mutate(SpeciesName = factor(SpeciesName,
                              levels = c(
                                "White Oak",
                                "Turkey Oak",
                                "Sweetgum",
                                "Red Maple",
                                "Shortleaf Pine",
                                "Slash Pine",
                                "Loblolly Pine",
                                "Longleaf Pine",
                                "Tulip Poplar"
                              )))

@@

```{r}
BA_plot_small <- before_after %>% 
  filter(MapCode %in% bp_mapcodes) %>%
  filter(CohortAge < 50) %>%
  group_by(pre_post, SpeciesName) %>%
  summarize(CohortAge_Avg = mean(CohortAge),
            CohortBiomass_Sum = sum(CohortBiomass)) %>%
  mutate(pre_post = factor(pre_post, levels = c("Initial Conditions",
                                                "Fire2-Dry",
                                                "Fire2-Wet",
                                                "Fire5-Dry",
                                                "Fire5-Wet",
                                                "No Scrapple"),
                           labels = c("Initial Conditions",
                                      "Fire2-Dry",
                                      "Fire2-Wet",
                                      "Fire5-Dry",
                                      "Fire5-Wet",
                                      "NoFire-Wet"))) %>%
  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
                                 SpeciesName=="SlashPine" ~ "Slash Pine",
                                 SpeciesName=="TulipTree" ~ "Tulip Poplar",
                                 SpeciesName=="RedMaple" ~ "Red Maple",
                                 SpeciesName=="SweetGum" ~ "Sweetgum",
                                 SpeciesName=="WhiteOak" ~ "White Oak",
                                 SpeciesName=="TurkeyOak" ~ "Turkey Oak",
                                 SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
  mutate(SpeciesName = factor(SpeciesName,
                              levels = c(
                                "White Oak",
                                "Turkey Oak",
                                "Sweetgum",
                                "Red Maple",
                                "Shortleaf Pine",
                                "Slash Pine",
                                "Loblolly Pine",
                                "Longleaf Pine",
                                "Tulip Poplar"
                              )))

bar_colors <- colorblind_pal()(8)[c(2,5,6,4,5,6,8)]
smalltrees_barchart <- BA_plot_small %>%
  ggplot() +
  geom_bar(stat="identity",aes(pre_post,CohortBiomass_Sum/1000, fill=SpeciesName)) +
  scale_fill_manual(values=bar_colors) +
  labs(x="LANDIS Run",
       y="Total Biomass (metric tons)",
       fill="Species") +
  theme_bw()
smalltrees_barchart

ggsave("biomass_smalltrees_barchart.jpg",path = here("Plots"), height=4)
```

```{r}
biomass <- (stacked_barchart / smalltrees_barchart +
  plot_layout(guides = "collect", axes = "collect") &
  theme(legend.position = "bottom",
        plot.tag.position = c(0.13,0.95))) +
  plot_annotation(tag_levels = "A")

# biomass
ggsave("biomass_barcharts.jpg", path = here("Plots"), height = 8, width = 5.1)
```
